\chapter*{Preface}
Explain which papers or other contributions are included in this thesis and where funding comes from.

This thesis contains the following papers.

\begin{paperlist}
    \item Meyers, Charles, Tommy L\"{o}fstedt, and Erik Elmroth. "Safety-critical computer vision: an empirical survey of adversarial evasion attacks and defenses on computer vision systems."
    \newblock {\em{Artificial Intelligence Review (2023): 1-35. [Impact Factor 12.0 in 2022] One sentence summary.}}
    
    \item Meyers, Charles, Tommy L\"{o}fstedt, and Erik Elmroth. “Massively Parallel Evasion Attacks and the Pitfalls of Adversarial Retraining.” 
    \newblock {\em{EAI Artificial Intelligence for Cybersecurity Conference. Bratislava, Slovakia (2023): 1-12.  [Received a Best Paper Award] One sentence summary.}}

    \item Charles Meyers, Mohammad Reza, Tommy L\"{o}fstedt and \\ Erik Elmroth. "A Training Rate and Survival Heuristic for Inference and Robustness Evaluation (TRASHFIRE)."
    \newblock {{\em{International Conference on Machine Learning and Cybernetics. Miyazaki, Japan. 11 pages.} One sentence summary.}}

    \item Charles Meyers, Mohammad Reza, Tommy L\"{o}fstedt and \\ Erik Elmroth. "A Cost-Aware Approach to Adversarial Robustness in Neural Networks."
    \newblock {\em{Journal, year. page numbers. One sentence summary.}}

    \item Charles Meyers, Aaron MacSween, Tommy L\"{o}fstedt and \\ Erik Elmroth. "Compression as  Kernel Metric."
    \newblock {\em {Journal, year. page numbers. One sentence summary.}}

    \item Charles Meyers, Mohammad Reza, Tommy L\"{o}fstedt and \\ Erik Elmroth. "Deckard: A tool for robust, declarative, and reproducible AI."
    \newblock {\em{Journal, year. page numbers. One sentence summary.}}
    
\end{paperlist}



\section*{Funding Statement}

Financial support has been provided in part by the Knut and Alice Wallenberg Foundation grant number 2019.0352 and by the eSSENCE Programme under the Swedish Government's Strategic Research Initiative.